Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-01 WSSSPE1_report/WSSSPE1_summary_report.tex
changing some footnotes to cites, a few other small edits in the keynote section

He has looked into reproducibility in computational biology, and has
concluded that ``I have proved I cannot reproduce research from my own
lab'':
(Computational
Biology Resources Lack Persistence And Usability, Veretnik, Fink and
Bourne.)\footnote{\url{http://www.ploscompbiol.org/article/info\%3Adoi\%2F10.1371\%2Fjournal.pcbi.1000136}} \todo{change this to a cite}

@@

He then presented the usual arguments on directly valuing software as a
research output alongside papers. Readers will be familiar with this
debate. An interesting reference here is ``What
does peer review mean when applied to computer code?, Rosemary Dickin.''
\footnote{\url{http://blogs.plos.org/biologue/2013/08/08/what-does-peer-review-mean-when-applied-to-computer-code/}} \todo{change to cite}

@@

He concluded with a reference to his paper
\footnote{\url{http://www.ploscompbiol.org/article/info\%3Adoi\%2F10.1371\%2Fjournal.pcbi.1002001}}``Ten
simple rules for getting ahead as a computational biologist in
academia'' \todo{change to cite} and argued that computational scientists ``have a
responsibility to convince their institutions and communities that
software is scholarship,'' a point with which we strongly agree.

@@

His talk used an example from data reduction in Astronomy, where one
attempts to remove interfering effects from the device. In this field, a
``bad pixel mask'' is recalculated by each researcher, despite being
persistent over time. He estimated 13 wasted person-years of waste.

He asked, of this practice, ``why didn't we know better?'' and argued
this was because we're taught to focus on immediate research outcomes
and not on continuously improving and building on tools for research. He
then asked, later in our working lives, when we do know better, why
don't we act any different, and argued this was due to incentivization:
only the immediate products of research, not the software, are valued.

>>>>

He has looked into reproducibility in computational biology, and has
concluded that ``I have proved I cannot reproduce research from my own
lab''~\cite{Veretnik}.

@@

He then presented the usual arguments on directly valuing software as a
research output alongside papers. Readers will be familiar with this
debate. An interesting reference here is ``What
does peer review mean when applied to computer code?, Rosemary Dickin.''
\footnote{\url{http://blogs.plos.org/biologue/2013/08/08/what-does-peer-review-mean-when-applied-to-computer-code/}}

@@

He concluded with a reference to his paper~\cite{bourne_ten} and argued that computational scientists ``have a
responsibility to convince their institutions and communities that
software is scholarship,'' a point with which we strongly agree.

@@

His talk used an example from data reduction in Astronomy, where he
needed to remove interfering effects from the device. He built a
``bad pixel mask'', and realized though while this is persistent, there
was no way/practice of sharing this with the data, so many researchers
repeated the same calculations. He estimated that 13 wasted person-years were wasted in
this redundant calculation.

He asked, of this practice, ``why didn't we know better?'' and argued
this was because we're taught to focus on immediate research outcomes
and not on continuously improving and building on tools for research. He
then asked, later in our working lives, when we do know better, why
don't we act any different, and argued this was due to incentives and their lack:
only the immediate products of research, not the software, are valued.
